### 2021-08-13 paper/paper.tex
"final time t" -> "final time T" for consistency

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. To make the mesh curvilinear, the interior of the box is heavily warped
by a combination of sine and cosine functions~\cite{chan2019efficient}. To integrate up to the
final time $t=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.

>>>>

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. To make the mesh curvilinear, the interior of the box is heavily warped
by a combination of sine and cosine functions~\cite{chan2019efficient}. To integrate up to the
final time $T=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.
